### 2017-12-12 Paper/main.tex
Updates from ShareLaTeX

\section{Evidence and findings}

\section{Conclusion}

>>>>

From such dataset we run the \textit{auto.arima} function and we isolated the fitting error. %inserire plot

In order to see the goodness of fitting we searched for autocorrelation on the residuals and we found any.

Then we built a NN out of it which set as input the lagged stock price and as output the current error term \ref{}.

After the model setting we set a series of condition that create the signal. Such condition are highlighted in the following diagram.

\section{Evidence and findings}
After 930 rounds, that is we run the sequence for all the stocks in the portfolio we get the following conclusion:
\begin{itemize}
    \item the model out perform the naive algorithm
    \item the model failed to predict in a consistent way whether the price was going up or down
    \item either the models alone failed to do so 
\end{itemize}
Therefore we can conclude that such model didn't gave any competitive advantage in terms of profit and loss.

\section{Conclusion}
In conclusion we can say that the hybrid ARIMA however is a very interesting tool for data forecasting is still not able (at least as posed in this paper) to be used in algorithmic trading.

The writer of this article hope that many other researchers will try to cast some light above this hybrd methodology in order to develop a better process for such modelling.

All the scripts and files are available on GitHub at the following repository:
